Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-21 docs/manuscript/manuscript.tex
Beginning to write the words for the water access typologies section.

\subsection*{Water accessibility typologies}
\hl{Show the typology/cluster results and discuss.}

>>>>

\subsection*{Water accessibility typologies}
\hl{Show the typology/cluster results and discuss.}
NBClust statistic analysis developed and determined four distinct groups. First cluster group composed of countries near the equator or in the Sub-Sahara Regions. The second analysis of the second group represents countries considered developed or recently industrialized.

%Results A gap statistic analysis resulted first in two distinct groups,with the first being composed of countries typically considered developed or newly industrialized.  The second analysis of the second group resulted in four country clusters. The greater subdivision would have resulted in statistically similar clusters, while greater aggregation would have resulted in highly internally heterogeneous clusters. The dendrogram resulting from this cluster analysis is shown in Fig. 1, and the corresponding gap curve yielding four clusters is shown in Fig. 2. Table 3 shows the resulting five water and sanitation country clusters. Fig. 3 shows the cluster country membership on a world map. The cluster indicator variable means are summarized in Table 4. The Dunn and Davies-BouldinIndices for our clusters, as well as the World Bank, WHO, and MDGgroupings are shown in Table 5. Our clusters have both the largest Dunn index and smallest Davies-Bouldin index, indicating that they represent a superior grouping along with the chosen relevant indicators.
